Chapter 2 Draft

### 2020-04-03 Rmd/Draft.Rmd
Olesen 2002 added with quantitative data

data2 <- readRDS("Data/RData/Spp_richness_by_order.RData")
clrs <- c("darkblue", "blue", "yellow", "cornsilk", "goldenrod",
          "orange")
par(mar = c(11,6.1,4.1,8))
barplot(data2, beside = FALSE, ylab = "% visits", cex.names = 0.5
        ,las = 2, col = clrs)
abline (h = 0)
par(xpd=TRUE)
leg <- c("Hymenoptera", "Coleoptera", "Lepidoptera", "Diptera", "Hemiptera")
legend(x = 35, y = 100, legend = rev(leg), cex = 0.4, fill = rev(clrs))
par(mar = c(5,1.1,4.1,2.1))
par(xpd=FALSE)

>>>>

data2 <- readRDS("Data/RData/Spp_richness_by_order.RData")
clrs <- c("darkblue", "blue", "yellow", "cornsilk", "goldenrod",
          "orange")
par(mar = c(11,6.1,4.1,8))
barplot(data2, beside = FALSE, ylab = "% Spp per order", cex.names = 0.5
        ,las = 2, col = clrs)
abline (h = 0)
par(xpd=TRUE)
leg <- c("Hymenoptera", "Coleoptera", "Lepidoptera", "Diptera", "Hemiptera")
legend(x = 35, y = 100, legend = rev(leg), cex = 0.4, fill = rev(clrs))
par(mar = c(5,1.1,4.1,2.1))
par(xpd=FALSE)
